Coherent Hyper-Raman Four Wave Mixing Spectroscopies

### 2024-06-11 paper.tex
shen90 exists!

To understand SR-SIVE selection rules more finely, the dipole and first hyperpolarizability operators are Taylor expanded in terms of an n$^{\text{th}}$ normal mode coordinate $Q_n$ about equilibrium: \cite{Long1970}
\begin{subequations}
	\begin{equation}
		\mu = \mu_0 + \frac{\partial \mu}{\partial Q_n} Q_n + \order{\sum_{m,n}{Q_m Q_n}}
	\end{equation}
	\begin{equation}
		\beta = \beta_{0} + \frac{\partial \beta}{\partial Q_n} Q_n + \order{\sum_{m,n}{Q_m Q_n}}
	\end{equation}
\end{subequations}
Substituting into \autoref{sivebeta} gives the SIVE-IR-I hyperpolarizability to $\order{Q_n}$ as \begin{equation}\label{SIVEselection}
		\gamma_{ijkl} =	-\frac{1}{\varepsilon_0} \frac{1}{24 \hbar}  \frac{1}{{\Delta_{gv}}} \ \frac{\partial \beta^{(ijk)}}{\partial Q_n} {\frac{\partial \mu^{(l)}}{\partial Q_n}}  (\mel{g}{Q_n}{v})^2\ \rho_{gg}
\end{equation}
Since this expression is non-zero in the harmonic oscillator limit, SR-SIVE output is allowed for harmonic transitions. 
Similar to SFG, SR-SIVE does not demand anharmonic ground state potential energy surfaces for spectral output. \cite{Shen94, Cho2000}
This selection rule is generally valid for any SR-SIVE process in the $-\vec{k}_1 + \vec{k}_2  + \vec{k}_3$ and $\vec{k}_1 + \vec{k}_2  + \vec{k}_3$ phasematching geometries when the Placzek approximation is valid.

@@

Most quantitative methods in an n$^{th}$ order CMDS experiment are used to extract $\chi^{(n)}$ values for comparing the relative strength of nonlinear processes in different media. \cite{Zhu87, RN351, RN345}
The recorded $\chi^{(n)}$ values provide insight into how microscopic quantities ($\vec{\mu}, \alpha_{ij}, \beta_{ijk}$) impact nonlinear output.
To our knowledge, only 2D-IR spectroscopy has taken advantage of orientationally averaged $\chi^{(3)}$ values to extract transition moments. \cite{Moilanen2009, RN245}
Previous treatments did not consider using quantitative analysis in SIVE to measure $\beta_{ijk}$ values from SIVE spectra.
It is thus useful to investigate how a simple treatment of orientational averaging can extract $\beta_{ijk}$ from a $\chi^{(3)}_{IJKL}$ expression.

>>>>

To understand SR-SIVE selection rules more finely, the dipole and first hyperpolarizability operators are Taylor expanded in terms of an n$^{\text{th}}$ normal mode coordinate $Q_n$ about equilibrium: \cite{Long1970}
\begin{subequations}
	\begin{equation}
		\mu = \mu_0 + \frac{\partial \mu}{\partial Q_n} Q_n + \order{{Q_m Q_n}}
	\end{equation}
	\begin{equation}
		\beta = \beta_{0} + \frac{\partial \beta}{\partial Q_n} Q_n + \order{{Q_m Q_n}}
	\end{equation}
\end{subequations}
Substituting into \autoref{sivebeta} gives the SIVE-IR-I hyperpolarizability to $\order{Q_n}$ as \begin{equation}\label{SIVEselection}
		\gamma_{ijkl} =	-\frac{1}{\varepsilon_0} \frac{1}{24 \hbar}  \frac{1}{{\Delta_{gv}}} \ \frac{\partial \beta^{(ijk)}}{\partial Q_n} {\frac{\partial \mu^{(l)}}{\partial Q_n}}  (\mel{g}{Q_n}{v})^2\ \rho_{gg}
\end{equation}
Since this expression is non-zero in the harmonic oscillator limit, SR-SIVE output is allowed for harmonic transitions. 
Similar to SFG, SR-SIVE does not demand anharmonic ground state potential energy surfaces for spectral output. \cite{Shen94, Cho2000}
This selection rule is generally valid for any SR-SIVE process in the $-\vec{k}_1 + \vec{k}_2  + \vec{k}_3$ and $\vec{k}_1 + \vec{k}_2  + \vec{k}_3$ phasematching geometries when the Placzek approximation is valid.

@@

Most quantitative methods in an n$^{th}$ order CMDS experiment are used to extract $\chi^{(n)}$ values for comparing the relative strength of nonlinear processes in different media. \cite{Zhu87, RN351, RN345}
The recorded $\chi^{(n)}$ values provide insight into how microscopic quantities ($\vec{\mu}, \alpha_{ij}, \beta_{ijk}$) impact nonlinear output.
To our knowledge, only vibraitonal SFG and 2D-IR spectroscopy has taken advantage of orientationally averaged $\chi^{(n)}$ values to extract transition moments. \cite{Shen90, Moilanen2009, RN245}
Previous treatments did not consider using quantitative analysis in SIVE to measure $\beta_{ijk}$ values from SIVE spectra.
It is thus useful to investigate how a simple treatment of orientational averaging can extract $\beta_{ijk}$ from a $\chi^{(3)}_{IJKL}$ expression.
